### 2024-10-11 project3/draft.tex
new

\begin{itemize} 
    \item GMMB contracts under stochastic volatility models. 
    \item GMWB contracts under the Black-Scholes model. 
    \item GMWB contracts under stochastic volatility models with different parameters.
\end{itemize}

>>>>

\begin{itemize} 
    \item GMMB contracts under a stochastic volatility asset model. 
    \item GMWB contracts under a Black-Scholes asset model. 
    \item GMWB contracts under a stochastic volatility model with different simulation parameters.
\end{itemize}
